\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-04-01 submission/manuscript.tex
Process optimization.

\usepackage[labelsep=period, labelfont=bf]{caption}
\renewcommand{\thefigure}{\arabic{figure}}
\captionsetup{justification=raggedright,singlelinecheck=false}

@@

\usepackage{siunitx}
\DeclareSIUnit\molar{\mole\per\cubic\deci\metre}
\DeclareSIUnit\Molar{\textsc{m}}

@@

@@

An alternative to these procedures is a direct isolation of the targeted
material by incubating macrophyte tissues in an extraction buffer. After
the incubation is done the undisrupted host tissue is removed and the
isolation procedure continues omitting host material contaminations. To
our knowledge the only procedure describing a direct and selective
epiphytic DNA isolation from the surfaces of marine macrophytes was
provided by Burke \emph{et al.} (2009). In contrast to previously
described methods this protocol enables an almost complete removal of
the surface community and was used for 16S rRNA gene clone libraries
construction (Burke \emph{et al.}, 2011b) and metagenomes sequencing
(Burke \emph{et al.}, 2011a). This method, thought providing a selective
isolation procedure, is using in the extraction buffer a rapid
multienzyme cleaner (3M) that is not worldwide available and whose
composition is not know (Burke \emph{et al.}, 2009). Also to our
knowledge, no selective isolation protocol for proteins from epiphytic
communities inhabiting marine macrophytes was established.

@@

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions (Wiśniewski \emph{et al.},
2009) with small modifications. Before loading the solution to the
column, protein pellets were solubilized in a urea sample buffer
included in the kit amended with DTT (final concentration 100
\si{\milli\Molar}) for 45 \si{\minute} at room temperature and
centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to
remove larger particles. The first washing step after protein solution
loading was repeated twice. In addition, centrifugation steps were
prolonged if the column was clogged. Trypsin digestion was performed on
column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}.
The final filtrate containing digested proteins was acidified with 1
\si{\percent} (final concentration) trifluoroacetic acid, freezed at
\num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent
to the Vienna Metabolomics Center (University of Vienna) for
metaproteomic analysis. Peptides were resuspended in 1 \si{\percent}
(final concentration) trifluoroacetic acid, desalted using the Pierce
C18 Tips (Thermo Fisher Scientific, USA) according to the manufacturer's
instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap
Mass Spectrometer (Thermo Fisher Scientific, USA). Obtained MS/MS
spectra were searched against a protein database from metagenomic
assembly published in Burke \emph{et al.} (2011a) using SEQUEST-HIT
engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo
Fisher Scientific, USA). The target-decoy approach was used to reduce
the probability of false peptide identification. Results whose false
discovery rate at the peptide level was \SI{< 1}{\percent} were kept.
For protein identification a minimum of of two peptides and one unique
peptide were required. For protein quantification, a chromatographic
peak area-based free quantitative method was applied.

@@

\leavevmode\hypertarget{ref-Burke2011a}{}%
Burke, C., Steinberg, P., Rusch, D., Kjelleberg, S., and Thomas, T.
(2011a) Bacterial community assembly based on functional genes rather
than species. \emph{Proceedings of the National Academy of Sciences of
the United States of America} \textbf{108}: 14288--14293.

\leavevmode\hypertarget{ref-Burke2011b}{}%
Burke, C., Thomas, T., Lewis, M., Steinberg, P., and Kjelleberg, S.
(2011b) Composition, uniqueness and variability of the epiphytic
bacterial community of the green alga Ulva australis. \emph{The ISME
journal} \textbf{5}: 590--600.

@@

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014) knitr: A Comprehensive Tool for Reproducible Research in
\{R\}. In, Stodden,V., Leisch,F., and Peng,R.D. (eds),
\emph{Implementing reproducible computational research}. Chapman;
Hall/CRC.

>>>>

\usepackage[labelsep=period, labelfont=bf]{caption}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\figurename}{Fig.}
\captionsetup{justification=raggedright,singlelinecheck=false}

@@

\usepackage{siunitx}
\DeclareSIUnit\molar{\mole\per\cubic\deci\metre}
\DeclareSIUnit\Molar{\textsc{m}}
\DeclareSIUnit\cells{\text{cells}}

@@

\usepackage{float}

\usepackage{xr}
\externaldocument[supp-]{supplementary}

\usepackage{txfonts}

\renewcommand{\figureautorefname}{Fig.}

@@

An alternative to these procedures is a direct isolation of the targeted
material by incubating macrophyte tissues in an extraction buffer. After
the incubation is done the undisrupted host tissue is removed and the
isolation procedure continues omitting host material contaminations. To
our knowledge the only procedure describing a direct and selective
epiphytic DNA isolation from the surfaces of marine macrophytes was
provided by Burke \emph{et al.} (2009). In contrast to previously
described methods this protocol enables an almost complete removal of
the surface community and was used for 16S rRNA gene clone libraries
construction (Burke and Thomas \emph{et al.}, 2011) and metagenomes
sequencing (Burke and Peter Steinberg \emph{et al.}, 2011). This method,
thought providing a selective isolation procedure, is using in the
extraction buffer a rapid multienzyme cleaner (3M) that is not worldwide
available and whose composition is not know (Burke \emph{et al.}, 2009).
Also to our knowledge, no selective isolation protocol for proteins from
epiphytic communities inhabiting marine macrophytes was established.

@@

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions (Wiśniewski \emph{et al.},
2009) with small modifications. Before loading the solution to the
column, protein pellets were solubilized in a urea sample buffer
included in the kit amended with DTT (final concentration 100
\si{\milli\Molar}) for 45 \si{\minute} at room temperature and
centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to
remove larger particles. The first washing step after protein solution
loading was repeated twice. In addition, centrifugation steps were
prolonged if the column was clogged. Trypsin digestion was performed on
column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}.
The final filtrate containing digested proteins was acidified with 1
\si{\percent} (final concentration) trifluoroacetic acid, freezed at
\num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent
to the Vienna Metabolomics Center (University of Vienna) for
metaproteomic analysis. Peptides were resuspended in 1 \si{\percent}
(final concentration) trifluoroacetic acid, desalted using the Pierce
C18 Tips (Thermo Fisher Scientific, USA) according to the manufacturer's
instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap
Mass Spectrometer (Thermo Fisher Scientific, USA). Obtained MS/MS
spectra were searched against a protein database from metagenomic
assembly published in Burke and Peter Steinberg \emph{et al.} (2011)
using SEQUEST-HIT engines and validated with Percolator in Proteome
Discoverer 2.1 (Thermo Fisher Scientific, USA). The target-decoy
approach was used to reduce the probability of false peptide
identification. Results whose false discovery rate at the peptide level
was \SI{< 1}{\percent} were kept. For protein identification a minimum
of of two peptides and one unique peptide were required. For protein
quantification, a chromatographic peak area-based free quantitative
method was applied.

@@

\leavevmode\hypertarget{ref-Burke2011a}{}%
Burke, C., Steinberg, P., Rusch, D., Kjelleberg, S., and Thomas, T.
(2011) Bacterial community assembly based on functional genes rather
than species. \emph{Proceedings of the National Academy of Sciences of
the United States of America} \textbf{108}: 14288--14293.

\leavevmode\hypertarget{ref-Burke2011b}{}%
Burke, C., Thomas, T., Lewis, M., Steinberg, P., and Kjelleberg, S.
(2011) Composition, uniqueness and variability of the epiphytic
bacterial community of the green alga Ulva australis. \emph{The ISME
journal} \textbf{5}: 590--600.

@@

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014) knitr: A Comprehensive Tool for Reproducible Research in
\{R\}. In \emph{Implementing reproducible computational research}.
Stodden, V., Leisch, F., and Peng, R.D. (eds). Chapman; Hall/CRC.
